\documentclass{report}

\title{Notes on General Topology}
\author{Wenchuan Zhao}
\input{head/head.tex}


\begin{document}
\maketitle
\tableofcontents

%========================================
%########################################
%----------------------------------------



\chapter{Topological Spaces}
%========================================


\section{Metric Spaces}
%----------------------------------------


How do we measure the distance between two points in a space? Take $\mathbb R^3$ for example, for any points $x, y \in \mathbb R^3$, the distance between $x$ and $y$ is usually means the length of the segments with $x$ and $y$ as its endpoints, which is given by
$$
\rho(x, y) = \left( \sum_{i = 1}^3 |x_i - y_i|^2 \right)^\frac{1}{2},
$$
where for any $p \in \mathbb R^3$, $p_i$ denotes the $i$-th component of $p$. Here, we consider $\rho$ as a function from $\mathbb R^3 \times \mathbb R^3$ to $\mathbb R$, called \textit{Euclidean metric function} on $\mathbb R^3$. Then, $\rho$ satisfies the following conditions: For any $x$, $y$, and $z \in \mathbb R^3$,
\begin{enumerate}
	\item $\rho(x, y) = 0$ if and only if $x = y$;
	\item $\rho(x, y) = \rho(y, x)$;
	\item $\rho(x, y) + \rho(y, z) \ge \rho(x, z)$; this property is also called \textit{triangle inequality}.
\end{enumerate}

In this case, we call the ordered pair $(\mathbb R^3, \rho)$ the \textit{$3$-dimensional Eulidean metric space}.

Just like how the first scientist defined the unite of 1 kilogram, a metric function is not entirely naturally given, but is chosen depend on what distance we need to find. In the example above, the set $\mathbb R^3$ can be replaced by any set $X$, and the metric function $\rho$ can be any operation from $X \times X \to \mathbb R$ satisfying the 3 conditions above. And this is how metric spaces are defined.

\begin{definition}
	Let $X$ be any set. A mapping $\rho: X \times X \to \mathbb R$ is a \textit{metric} on $X$ if and only if it satisfies the \textit{metric axioms}. That is, for any $\mathbf x, \mathbf y, \mathbf z \in X$,
	\begin{enumerate}[(M1)]
		\item $\rho(x, y) = 0$ if and only if $x = y$;
		\item $\rho(x, y) = 0$ if and only if $x = y$;
		\item $\rho(x, y) + \rho(y, z) \ge \rho(x, z)$.
	\end{enumerate}
	
	An ordered pair $(X, \rho)$ is a \textit{metric space} if and only if $\rho$ is a metric on $X$.
\end{definition}

Some author also consider $\rho(x, y) \ge 0$ as an axiom in the list above, but, rigorously, it is a property deduced by the 3 axioms. By metric axiom M3, we have
$$
\rho(x, y) + \rho(y, x) \ge \rho (x, x).
$$
By M2, we have
$$
\rho(x, y) + \rho(x,y) \ge \rho(x, x).
$$
By M1, we have
$$
2\rho (x,y) \ge 0.
$$
Thus,
$$
\rho(x,y) \ge 0.
$$

So, if we are going to prove if an operation is a metric, this is an unnecessary progress.


\begin{definition}
	Let $(X, \rho)$ be a metric space, let $x \in X$, and let $\delta \in \mathbb R_{> 0}$.

	The \textit{open $\delta$-ball}, or simply \textit{$\delta$-ball}, of $x$ is defined as the set
	$$
	B(x, \delta) = \left\{ y \in X: \rho(x,y) < \delta \right\}.
	$$
\end{definition}


The “shape” of an open ball is determined by the metric and the set. In the 3-dimensional Euclidean metric space $(\mathbb R^3, \rho)$, for example, an open $\delta$-ball of $x$ is a sphere with $x$ as its center and $\delta$ as its radius. But if $\rho$ is a \textit{taxicap metric} on $\mathbb R^3$, i.e.,
$$
\rho(x,y) = |x_1 - y_1| + |x_2 - y_2| + |x_3 - y_3|,
$$
then, an open $\delta$-ball of $x$ is no longer a sphere, but a box with $x$ as its center and $2\delta$ as the length of it edges.

If $<$ is replaced by $\le$ in the definition, then we have the definition blew.


\begin{definition}
	Let $(X, \rho)$ be a metric space, let $x \in X$, and let $\delta \in \mathbb R_{> 0}$.
	
	The \textit{closed $\delta$-ball} of $x$ is defined as the set
	$$
	\overline B(x, \delta) = \left\{ y \in X: \rho(x,y) \le \delta \right\}.
	$$
\end{definition}


Note that, in the both definitions above, we have the condition $y \in X$. This means, open (closed) balls are always subsets of $X$. For example, let
$$
X = [0 , 1] \times [0,1],
$$
and let $\rho$ be an Euclidean metric on $X$. In this case, $B(0,1)$ is not a disk, but disk sector.


\section{Some Examples on Metric Spaces}
%----------------------------------------


\begin{example}
	Some metrics do not care about the any geometrical length. For example, let $\rho: \mathbb R_{> 0} \times \mathbb R_{> 0} \to \mathbb R$ be defined as
	$$
	\rho(x,y) =
	\begin{cases}
	\displaystyle \frac{x}{y} - 1 &: x \ge y; \\
	\displaystyle \frac{y}{x} - 1 &: x < y,
	\end{cases}
	$$
	then $\rho$ is a metric on $\mathbb R_{> 0}$ only cares about the ratio between any two points in the space.
	
	There is another metric on $\mathbb R_{> 0}$ which is quite similar. Let $\rho: \mathbb R_{> 0} \times \mathbb R_{> 0} \to \mathbb R_{\ge 0}$ be defined as
	$$
	\rho(x,y) = \left|\log \left( \frac{x}{y} \right) \right|,
	$$
	then $\rho$ is a metric on $\mathbb R_{> 0}$, and it can be proved by the properties of logarithm functions.
\end{example}


\begin{example}
	The \text{discrete metric} $\rho$ on $X$ only cares about if any two points $x$ and $y$ in $X$ coincide or not. That is,
	$$
	\rho(x,y) =
	\begin{cases}
	1 &: x \ne y; \\
	0 &: \text{else}.
	\end{cases}
	$$
\end{example}


\begin{example}
	The 3-dimensional Euclidean metric space is one of $p$-product metric spaces. Let
	$$
	X = \prod_{i = 1}^n X_i.
	$$
	Then, for any $p \in \mathbb R_{\ge 1}$, the $p$-product metric $\rho_p: \mathbb R^n \times \mathbb R^n \to \mathbb R$ is defined as
	$$
	\rho_p(x, y) = \left( \sum_{i = 1}^n \rho_i^p(x_i, y_i) \right)^\frac{1}{p},
	$$
	where $\rho_i(x_i, y_i)$ can be the Euclidean metric on $X_i$ for any $i \in \{1, \ldots, n\}$, but it is not required. Indeed, $p$-product metric spaces are metric space. It is easy to show that $\rho_p$ satisfies the metric axiom 1 and 2. Now, we prove that the $\rho_p$ satisfies the metric axiom 3. That is to show that
	$$
	\left( \sum_{i = 1}^n \rho_i(x_i, z_i)^p \right)^\frac{1}{p} \le \left( \sum_{i = 1}^n \rho_i(x_i, y_i)^p \right)^\frac{1}{p} + \left( \sum_{i = 1}^n \rho_i(y_i, z_i)^p \right)^\frac{1}{p}
	$$
	for any $x,y,z \in X$.
	
	\begin{proof}
		By Minkowski's inequality,
		$$
		\left( \sum_{i = 1}^n (\rho_i (x_i, y_i) + \rho_i(y_i, z_i))^p \right)^\frac{1}{p} \le \left( \sum_{i = 1}^n \rho_i(x_i, y_i)^p \right)^\frac{1}{p} + \left( \sum_{i = 1}^n \rho_i(y_i, z_i)^p \right)^\frac{1}{p}.
		$$
		As for any $i$, $\rho_i$ is a metric on $X_i$. So $\rho_i$ satisfies the open axiom 3. Thus,
		$$
		\left( \sum_{i = 1}^n \rho_i(x_i, z_i)^p \right)^\frac{1}{p} \le \left( \sum_{i = 1}^n (\rho_i (x_i, y_i) + \rho_i(y_i, z_i))^p \right)^\frac{1}{p}.
		$$
		That is,
		$$
		\rho(x, z) \le \rho(x,y) + \rho(y,z),
		$$
		which is precisely the metric axiom 3.
	\end{proof}
\end{example}



\begin{example}
	Let $M$ be a set of all bounded functions $S \to (T, \rho_T)$, where $\rho_T$ is a metric on $T$. Here, we treat all of these functions as points in $M$. Let $\rho: M \times M \to \mathbb R$ be defined as
	$$
	\rho(f,g) = \sup_{x \in S} \rho_T(f(x), g(x)),
	$$
	Then $\rho$ is a metric on $M$. It is actually easy to prove that $\rho$ is indeed a metric on $M$. Take the metric axiom 3 for example.
	
	\begin{proof}
		Let $f, g, h \in M$, then we have
		$$
		\begin{aligned}
		\rho(f, g) + \rho(g, h) &= \sup_{x \in S} \rho_T(f(x), g(x)) + \sup_{x \in S} \rho_T (g(x), h(x)) \\
		&= \sup_{x \in S} \left( \rho_T (f(x), g(x)) + \rho_T (g(x), h(x)) \right).
		\end{aligned}
		$$
		As $\rho_T$ satisfies the metric axiom 3, we have
		$$
		\ldots \ge \sup_{x \in S} \rho(f(x), h(x)) = \rho(f,h).
		$$
	\end{proof}
\end{example}


\begin{example}
	Let $(M, \rho)$ be a metric space. Let $\rho_H: \mathcal P(M) \setminus \{\emptyset\} \to \mathbb R$ be defined as
	$$
	\rho_H(X, Y) = \max \left\{ \sup_{x \in X} \rho(x, Y), \sup_{y \in Y} \rho (y, X) \right\},
	$$
	where
	$$
	\rho_H(a, B) = \inf_{b \in B} \rho(a,b).
	$$
	
	$\rho_H$ is called \textit{Hausdorff metric}. It measures how two subsets $X$ and $Y$ of $M$ are similar.
\end{example}



\section{Topological Spaces}
%----------------------------------------

There are actually at least two ways to define topological spaces: by open set axioms or by bases of sets. The definition by open set axioms might be the more popular one.

\begin{definition}
	\label{def: topology}
	
	Let $X$ be any set.
	
	A collection $\mathcal T \subseteq \mathcal P(X)$ is a \textit{topology} for $X$ iff it satisfies the \textit{open set axioms}:
	\begin{enumerate}[(O1):]
		\item
		$X \in \mathcal T$;
		
		\item
		$\mathcal T$ is closed under arbitrary union; explicitly,
		$$
		\forall \mathcal U \subseteq \mathcal T: \bigcup \mathcal U \in \mathcal T;
		$$
		
		\item
		$\mathcal T$ is closed under finite intersection; explicitly,
		$$
		\forall \mathcal F \subseteq \mathcal T : |\mathcal F| \in \mathbb N : \bigcap \mathcal F \in \mathcal T.
		$$
	\end{enumerate}
	
	The ordered pair $(X, \mathcal T)$ is a \textit{topological space} iff $\mathcal T$ is a topology for $X$.
		
	A subset $U \subseteq X$ is an \textit{open set} of $(X, \mathcal T)$, or an \textit{open subset} of $X$, iff $U \in \mathcal T$.
\end{definition}


Another way to define topological spaces is to consider any topological space as a collection \textit{generated} by a basis of the given set. Given any set $X$, a basis $\mathcal B$ of $X$ is a cover of $X$, where for any $A, B \in \mathcal B$, $A \cap B$ can be considered as the union of an $\mathcal S \subseteq \mathcal B$; i.e.,
$$
A \cap B = \bigcup \mathcal S.
$$

For example, if $(X, \rho)$ is a metric space, then the set of all open balls in $(X, \rho)$ is a basis of $X$.

\begin{lemma}
	Let $X$ be any set, and let $\mathcal T \subseteq \mathcal P(X)$.
	
	Then, $\mathcal T$ is a topology for $X$ if and only if there exists a basis $\mathcal B$ of $X$ such that
	$$
	\mathcal T = \left\{ \bigcup \mathcal A: \mathcal A \subseteq \mathcal B \right\}.
	$$
	
	\begin{proof}
		Assume $\mathcal T$ is a topology for $X$, then $\mathcal T$ itself is a basis of $X$. (Why?) Then, $\mathcal T \subseteq \left\{ \bigcup \mathcal A : \mathcal A \subseteq \mathcal T \right\}$. But, As $\mathcal T$ satisfies the open axiom 2, for any $\mathcal A \subseteq \mathcal T$, $\bigcup \mathcal A \in \mathcal T$, thus $\mathcal T \supseteq \left\{ \bigcup \mathcal A : \mathcal A \subseteq \mathcal T \right\}$.
		Thus, $\mathcal T = \left\{ \bigcup \mathcal A : \mathcal A \supseteq \mathcal T \right\}$.
		\qedlm
		
		On the other hand, assume there is a basis $\mathcal B$ of $X$ such that $\mathcal T = \left\{ \bigcup \mathcal A: \mathcal A \subseteq \mathcal B \right\}$.
		
		As $\mathcal B$ is a cover of $X$ and $\mathcal B \subseteq \mathcal B$, we have $X = \bigcup \mathcal B \in \mathcal T$. So $\mathcal T$ satisfies the open set axiom O1.
		
		Let $\mathcal U \subseteq \mathcal T$. For any $U \in \mathcal U$, let $\mathcal A_U \subseteq \mathcal B$ such that $U = \bigcup \mathcal A_U$. Thus
		$$
		\begin{aligned}
			\bigcup \mathcal U &= \bigcup_{U \in \mathcal U} \left( \bigcup \mathcal A_U \right) = \bigcup \left( \bigcup_{U \in \mathcal U} \mathcal A_U \right).
		\end{aligned}
		$$
		The union in the bracket is a subset of $\mathcal B$, so $\bigcup \mathcal U \in \mathcal T$. Thus, open set axiom 2 is satisfied.
		
		Let $U, V \in \mathcal T$. Then there exist $\mathcal U, \mathcal V \subseteq \mathcal B$ such that $U = \bigcup \mathcal U$ and $V = \bigcup \mathcal V$. Then, we have
		$$
		\begin{aligned}
			A \cap B &= \bigcup \mathcal U \cap \bigcup \mathcal V \\
			&= \bigcup_{U \in \mathcal U} \left( U \cap \bigcup \mathcal V \right) \\
			&= \bigcup_{U \in \mathcal U} \left( \bigcup_{V \in \mathcal V} (U \cap V) \right).
		\end{aligned}
		$$
		
		As $\mathcal B$ is a basis of $X$, there exists for any $U, V \in \mathcal B$, there exists a $\mathcal O_{(U,V)} \subseteq \mathcal B$, such that
		$$
		U \cap V = \bigcup \mathcal O_{(U, V)}.
		$$
		Thus, we have
		$$
		\begin{aligned}
			A \cap B &= \bigcup_{(U, V) \in \mathcal U \times \mathcal V} \left( \bigcup \mathcal O_{(U, V)} \right) \\
			&= \bigcup \left( \bigcup_{(U, V) \in \mathcal U \times \mathcal V} \mathcal O_{(U, V)} \right).
		\end{aligned}
		$$
		
		The union in the bracket is a subset of $\mathcal B$, thus $A \cap B \in \mathcal T$. Then, the open set axiom 3 is satisfied.
	\end{proof}
\end{lemma}

For any set $X$, we say that a topology $\mathcal T$ for $X$ is \textit{generated} by a basis $\mathcal B$ of $X$ if and only if $\mathcal T$ can be considered as $\{\bigcup \mathcal A: \mathcal A \subseteq \mathcal B\}$.


====


Even if $\mathcal T$ is an infinite	topology on an infinite set $X$, $\mathcal T$ is not needed to be closed under infinite intersection. For example, let $\mathcal T$
$$
\mathcal T = \left\{ [0,r): r \in \mathbb R \right\}.
$$
then $\mathcal T$ is a topology for $\mathbb R_{\ge 0}$. The collection
$$
\left\{ \left[ 0, \frac{1}{i} \right) \right\}_{i \in \mathbb Z_{> 0}}
$$
is a subset of $\mathcal T$, but its intersection is $\{0\} \notin \mathcal T$.



\begin{lemma}
	\label{lm: emptyset is in topology}
	
	Let $(X, \mathcal T)$ be a topological space.
	
	Then, $\emptyset \in \mathcal T$.
\end{lemma}


\begin{proof}
	As $\emptyset$ is a subset of any set, $\emptyset \subseteq \mathcal T$. By the open set axiom 2, we have
	$$
	\emptyset = \bigcup \emptyset \in \mathcal T.
	$$
\end{proof}


\begin{example}
	Let $X = \{1, 2, 3\}$, and let
	$$
	\mathcal B = \{\{1,2\}, \{2, 3\}, \{2\}\},
	$$
	and let $\mathcal T = \{\bigcup \mathcal A: \mathcal A \subseteq \mathcal B\}$, then $\mathcal T$ is a topology for $X$.
\end{example}


\begin{definition}
	Let $X$ be any set, and let $\mathcal T_1$ and $\mathcal T_2$ be topologies on $X$.
	
	$\mathcal T_1$ is said to be \textit{finer} than $\mathcal T_2$, or $\mathcal T_2$ is said to be \textit{coarser} than $\mathcal T_1$ iff $\mathcal T_2 \subseteq \mathcal T_1$.
\end{definition}


\begin{example}
	For any set $X$, the power set $\mathcal P(X)$ can be considered as a topology for $X$, called \textit{discrete topology}. It is the \textit{finest topology} on $X$.
\end{example}

\begin{example}
	For any set $X$, the collection $\{\emptyset, X\}$ is a topology for $X$. It is called \textit{indiscrete topology}, or \textit{trivial topology}, which is the coarsest topology on $X$.
\end{example}


\section{Interiors and Closures}
%----------------------------------------


\begin{definition}
	Let $(X, \mathcal T)$ be a topological space, and let $U \subseteq X$.
	
	The \textit{interior} of $A$, denoted $A^\circ$ or $\mathrm{int} (A)$, in $(X, \mathcal T)$ is defined as the union of all open sets contained in $A$. Explicitly, $\mathrm{int}_X$ can be considered as a mapping from $\mathcal P(X)$ to $\mathcal P(X)$, defined as
	$$
	\mathrm{int}_X(A) := \bigcup (\mathcal P(A) \cap \mathcal T).
	$$
\end{definition}


\begin{note}
	Finding the interior of a subset requires the definition of the topology for the set. I mean, even for the same set $X$ and the same subset $A \subseteq X$, if there are two different topologies $\mathcal T_1$ and $\mathcal T_2$ for $X$, the interior of $A$ in $(X, \mathcal T_1)$ and $(X, \mathcal T_2)$ might be different. For example, in $\mathbb R$, let $\mathcal T_1$ be indiscrete topology for $\mathbb R$, and let $\mathcal T_2$ be the Euclidean topology for $\mathbb R$, then,
	$$
	\mathrm{int}_{\mathcal T_1} ([0,1)) = \emptyset, \text{ and } \mathrm{int}_{\mathcal T_2}([0,1)) = (0,1),
	$$
	where $\mathrm{int}_{\mathcal T_1}(\cdot)$ and $\mathrm{int}_{\mathcal T_2}(\cdot)$ denotes the interior mapping for $(X, \mathcal T_1)$ and $(X, \mathcal T_2)$ respectively.
\end{note}


\begin{note}
	By the definition, it is clear that for any topology $(X, \mathcal T)$ and for any $A \subseteq X$, $\mathrm{int}(A) \in \mathcal T$.
\end{note}


\begin{lemma}
	Let $(X, \mathcal T)$ be a topological space, let $A \subseteq X$, and let $U \in \mathcal T$.
	
	Then, $U \subseteq A$ if and only if $U \subseteq \mathrm{int}(A)$.
	
	\begin{proof}
		As $U \in \mathcal P(A)$ and $U \in \mathcal T$, $U \in \mathcal P(A) \cap \mathcal T$. Thus,
		$$
		U \subseteq \bigcup \mathcal (\mathcal P(A) \cap \mathcal T) = \mathrm{int}(A).
		$$
		\qedlm
		
		Conversely, as $\mathrm{int}(A) \subseteq A$, as $U \subseteq \mathrm{int}(A)$, $U \subseteq A$.
	\end{proof}
\end{lemma}


\begin{lemma}
	Let $(X, \mathcal T)$ be a topological space, and let $A \subseteq X$.
	
	$\mathrm{int}(A) = A$ if and only if $A \in \mathcal T$.
	
	\begin{proof}	
		If $\mathrm{int}(A) = A$, then $A = \bigcup (\mathcal P (A) \cap\mathcal T)$. As $\mathcal P(A) \cap \mathcal T \subseteq \mathcal T$, this union is an element of $\mathcal T$.
		\qedlm
		
		Conversely, as $A \in \mathcal P(A)$ and $A \in \mathcal T$, $A \in \mathcal P(A) \cap \mathcal T$. For any $U \in \mathcal P(A)$, $U \subseteq A$. Then, we have $A \supseteq \bigcup (\mathcal P(A) \cap \mathcal T)$; and as $A \subseteq \bigcup (\mathcal P(A) \cap \mathcal T)$, we have
		$$
		A = \bigcup (\mathcal P(A) \cap \mathcal T) = \mathrm{int}(A).
		$$
	\end{proof}
\end{lemma}


\begin{lemma}
	Let $(X, \mathcal T)$ be a topological space, and let $A, B \subseteq X$.
	
	Then,
	$$
	\mathrm{int}(A \cap B) = \mathrm{int}(A) \cap \mathrm{int}(B).
	$$
	
	\begin{proof}
		Let $U \subseteq \mathrm{int}(A \cap B)$. Then,
		$$
		\begin{aligned}
			U \subseteq \mathrm{int}(A \cap B) = \bigcup (\mathcal P(A \cap \mathcal B) \cap \mathcal T).
		\end{aligned}
		$$
		
		Note that $\mathcal P(A \cap B) = \mathcal P(A) \cap \mathcal P(B)$, so $U \in \mathcal P(A \cap B) \cap \mathcal T$ iff $U \in \mathcal P(A) \cap \mathcal T$ and $\mathcal P(B) \cap \mathcal T$. We have
		$$
		\begin{aligned}
			U \subseteq \bigcup (\mathcal P(A \cap \mathcal B) \cap \mathcal T) &\iff U \subseteq \bigcup (\mathcal P(A) \cap \mathcal T) \land U \subseteq \bigcup (\mathcal P(B) \cap \mathcal T) \\
			&\iff U \subseteq \mathrm{int}(A) \land U \subseteq \mathrm{int}(B) \\
			&\iff U \subseteq \mathrm{int}(A) \cap \mathrm{int}(B).
		\end{aligned}
		$$
		
		Thus, $\mathrm{int}(A \cap B) = \mathrm{int}(A) \cap \mathrm{int}(B)$.
	\end{proof}
\end{lemma}



\section{Bases for Topologies}
%----------------------------------------


\begin{definition}
	Let $(X, \mathcal T)$ be a topological space.
	
	A collection $\mathcal B \subseteq \mathcal T$ is an \textit{analytic basis} for $\mathcal T$ iff for any $U \in \mathcal T$, there is an $\mathcal A \subseteq \mathcal B$, such that
	$$
	U = \bigcup \mathcal A.
	$$
\end{definition}


\begin{lemma}
	Let $(X, \mathcal T)$ be a topological space.
	
	A collection $\mathcal B \subseteq \mathcal T$ is an analytic basis for $\mathcal T$ iff for any $U \in \mathcal T$ and for any $x \in U$, there exists a $B \subseteq \mathcal B$, such that
	$$
	x \in B \subseteq \mathcal B.
	$$
\end{lemma}


\begin{proof}
	Let $\mathcal B$ be an analytic basis for $\mathcal T$.
	
	As $\mathcal B$ is a basis for $\mathcal T$, for any $U \in \mathcal T$, there exists a $B' \subseteq \mathcal B$ such that $U = \bigcup \mathcal B'$, which implies that for any $B' \in \mathcal B$, $B' \subseteq U$.
	
	$\qedlm$
	
	Conversely, let $\mathcal B \subseteq \mathcal T$ satisfies the condition after ``iff".
	
	Let $U \in \mathcal T$. For any $x \in U$, let $B_x \in \mathcal B$ with $x \in B_x \subseteq U$.
	
	As $\bigcup \{x\}_{x \in U} = U$, and $\{x\} \subseteq B_x$, we have
	
	$$
	U \subseteq \bigcup_{x \in U} B_x.
	$$
	
	As every $B_x \subseteq U$, we have
	$$
	\bigcup_{x \in U} B_x \subseteq U.
	$$
	Thus,
	$$
	U = \bigcup_{x \in U} B_x.
	$$
\end{proof}


=======


\begin{note}
	Explicitly, 2 can be considered as: for any $B_1, B_2 \in \mathcal B$, and for any $x \in B_1 \cap B_2$, there exists a $B_x \in \mathcal B$, such that
	$$
	x \in B_x \subseteq B_1 \cap B_2.
	$$
	(Why?)
\end{note}


\begin{note}
	$\emptyset$ is not necessary be an element of $\mathcal B$.
\end{note}


\begin{lemma}
	Let $(X, \mathcal T)$ be a topological space, and let $\mathcal B$ be an analytic basis for $\mathcal T$.
	
	Then, $\mathcal B$ is a synthetic basis of $X$.
\end{lemma}


\begin{proof}
	Let $B_1, B_2 \in \mathcal B$.

	As $\mathcal B$ is an analytic basis for $\mathcal T$, $\mathcal B \subseteq \mathcal T$, thus $B_1 \cap B_2 \in \mathcal T$.
	
	Thus, there exists an $\mathcal A \subseteq \mathcal B$, such that
	$$
	B_1 \cap B_2 = \bigcup \mathcal A.
	$$
	
	This precisely satisfies the definition of synthetic basis.
\end{proof}


\begin{lemma}
	Let $X$ be any set, and let $\mathcal B$ be a synthetic basis of $X$.
	
	Let
	$$
	\mathcal T = \left\{ \bigcup \mathcal A : \mathcal A \subseteq \mathcal B  \right\}.
	$$
	
	Then, $\mathcal T$ is a topology for $X$.
\end{lemma}


\begin{proof}
	As $\mathcal B$ is a synthetic basis of $X$, $X \subseteq \bigcup \mathcal B$. As $\mathcal B \subseteq \mathcal P(X)$, $\bigcup \mathcal B \subseteq X$. Thus, $X = \bigcup \mathcal B \in \mathcal T$.
	\qedlm

	Let $\mathcal U \subseteq \mathcal T$. For any $U \in \mathcal U$, there exists an $\mathcal A_U \subseteq \mathcal B$, such that $U = \bigcup \mathcal A_U$.
	
	We have
	$$
	\begin{aligned}
		\bigcup \mathcal U &= \bigcup \left\{ \bigcup \mathcal A_U \right\}_{U \in \mathcal U} \\
		&= \bigcup \left( \bigcup \left\{ \mathcal A_U \right\}_{U \in \mathcal U} \right)
	\end{aligned}
	$$
	
	As for any $U \in \mathcal U$, $\mathcal A_U \subseteq \mathcal B$, thus,
	$$
	\mathcal U = \bigcup \left\{ \mathcal A_U \right\}_{U \in \mathcal U} \subseteq \mathcal B.
	$$
	
	Thus, $\bigcup \mathcal U \in \mathcal T$. Therefore, $\mathcal T$ is closed under arbitrary union.
	\qedlm
	
	Let $\mathcal V$ be a finite subset of $\mathcal T$. For any $V \in \mathcal U$, there exists an $\mathcal A_V \subseteq \mathcal B$, such that $U = \mathcal A_V$.
	
	We have
	$$
	\begin{aligned}
		\bigcap \mathcal V &= \bigcap \left\{ \bigcup \mathcal A_V \right\}_{V \in \mathcal U} \\
		&= \bigcap \left( \bigcup \left\{ \mathcal A_V \right\}_{V \in \mathcal U} \right).
	\end{aligned}
	$$
	
	Similar to what we have proved above,
	$$
	\mathcal V = \bigcup \{\mathcal A_V\}_{V \in \mathcal V} \subseteq \mathcal B.
	$$
	
	Thus, $\bigcap \mathcal V \in \mathcal T$. Therefore, $\mathcal T$ is closed under finite intersection.
\end{proof}


\begin{lemma}
	Let $X$ be any set, and let $\mathcal C$ be a cover of $X$.
	
	The collection
	$$
	\mathcal B = \left\{ \bigcap \mathcal A: \mathcal A \subseteq \mathcal C \land |\mathcal A| \in \mathbb N \right\}
	$$
	is a synthetic basis of $X$.
\end{lemma}


\begin{proof}
	Let $B_1, B_2 \in \mathcal B$. There exist $\mathcal U, \mathcal V \subseteq \mathcal C$, such that $B_1 = \bigcup \mathcal U$ and $B_2 = \bigcup \mathcal V$. Then, we have
	$$
	\begin{aligned}
		B_1 \cap B_2 &= \bigcup_{U \in \mathcal U} U \cap \bigcup_{V \in \mathcal V} V \\
		&= \bigcup \{ U \cap V \}_{U \in \mathcal U, V \in \mathcal V}.
	\end{aligned}
	$$
	
	$\{U, V\} \subseteq \mathcal C$, so $U \cap V \in \mathcal B$. As $U$ and $V$ are arbitrarily taken from $\mathcal U$ and $\mathcal V$ respectively, $\{ U \cap V \}_{U \in \mathcal U, V \in \mathcal V} \subseteq \mathcal B$.
	
	Therefore, for any $B_1, B_2 \in \mathcal B$, there exists a finite $\mathcal A \subseteq \mathcal B$, such that $B_1 \cap B_2 = \bigcap \mathcal A$.
\end{proof}


\begin{note}
	In this note, we say that $\mathcal C$ \textit{generates} $\mathcal B$.
\end{note}


\begin{note}
	If $\mathcal C$ generates the synthetic basis $\mathcal B$, then $\mathcal B$ is the smallest synthetic basis containing $\mathcal C$. (Why?)
\end{note}


\begin{definition}
	Let $(X, \mathcal T)$ be a topological space, and let $\mathcal B$ be a synthetic basis of $X$.
	
	$\mathcal T$ is \textit{generated by} $\mathcal B$ iff
	$$
	\mathcal T = \left\{ \bigcup \mathcal A: \mathcal A \subseteq \mathcal B \right\}.
	$$
\end{definition}



\begin{example}
	In $\mathbb R^n$, for any $\mathbf x \in \mathbb R^n$, define
	$$
	B(\mathbf x, \delta) = \{ \mathbf y \in \mathbb R^n : \| \mathbf x - \mathbf y \| < \delta \land \delta \in \mathbb R_{> 0} \}.
	$$
	Let $\mathcal B$ be the set of all such $B(\mathbf x, \delta)$, then, $\mathcal B$ is a synthetic basis of $\mathbb R^n$, and it generates the \textit{Euclidean topology} for $X$.
\end{example}


\begin{example}
	In $\mathbb R^n$, let $\mathcal I$ be the set of all open intervals. $\mathcal I$ is a synthetic basis of $\mathbb R^n$, and it also generates the Euclidean topology for $\mathbb R^n$.
\end{example}


\begin{example}
	An \textit{ordered set} $(X, \preceq)$ is a set $X$ together with an \textit{ordering} $\preceq$ defined on $X$. That is, for any $x, y, z \in X$,
	\begin{enumerate}[(i)]
		\item
		(reflexive) $x \preceq x$;
		
		\item
		(transitive) $x \preceq y$ and $y \preceq z$ implies $x \prec z$;
		
		\item
		(antisymmetric) $x \preceq y$ and $y \preceq x$ implies $x = y$.
	\end{enumerate}
	
	$(X, \preceq)$ is an \textit{totally ordered set} iff $\preceq$ is \textit{connected}. That is, for any $x,y \in X$, $x \ne y$ implies $x\prec y$ or $y \prec x$.
	
	Now, let $(X, \preceq)$ be a totally ordered set, and let
	$$
	\mathcal A = \left\{X_{\prec x} : x \in X \right\} \cup \left\{ X_{\succ x} : x \in X \right\}.
	$$
	
	Let $\mathcal B$ be the synthetic basis generated by $\mathcal A$.
	
	Then, $\mathcal B$ generates an \textit{order topology} for $X$.
	
	If $\preceq$ is $\le$ on $\mathbb R$, then, the order topology for $\mathbb R$ is exactly the same as its Euclidean topology.
	
	Let
	$$
	\mathcal X = \left\{ \prod_{i = 1}^n \mathbb R_{< x_i} \right\} \cup \left\{ \prod_{i = 1}^n \mathbb R_{> x_i} \right\},
	$$
	let $\mathcal B$ be the synthetic basis for $\mathbb R^n$ generated by $\mathcal X$. Then $\mathcal B$ also generates the Euclidean topology for $\mathbb R^n$
\end{example}


\begin{note}
	In the example above, if $(X, \preceq)$ is an ordered set, but the connectedness of $\preceq$ is not required, then $\mathcal A$ is not a cover of $X$, and it generates no synthetic basis of $X$.
\end{note}


\begin{example}
	For any totally ordered set $(X, \preceq)$, the discrete topology for $X$ can be generated by either the collection of all closed intervals in $X$ or the collection of all singletons in $X$.
\end{example}


\begin{example}
	Let $(X, \preceq)$ be a totally ordered set, and let $C$ be a countable subset of $X$. The set
	$$
	\mathcal A = \{ X_{\prec x} : x \in C \}
	$$
	is a countable synthetic basis of $X$, and it generates a countable topology for $X$.
\end{example}


\begin{example}
	Let $X$ be an countably infinite set, and let $\mathcal B$ be the partition of $X$. As $\mathcal B$ is a synthetic basis for $X$, let $\mathcal T$ be the topology generated by $\mathcal B$.
	
	Then, $|\mathcal T| = |\mathcal P(\mathcal B)| = 2^{|\mathcal B|}$. Thus,
	\begin{enumerate}[(i)]
		\item $\mathcal T$ is finite iff $\mathcal B$ is finite;
		\item $\mathcal T$ is uncountable iff $\mathcal B$ is infinite (even if $\mathcal B$ is just countably infinite).
		\item $\mathcal T$ can not be countably infinite.
	\end{enumerate}
\end{example}



































%----------------------------------------
%########################################
%========================================
\end{document}